The Private School Network

### 2024-02-22 index.qmd
#15 update title + level-1 slides

---
title: "The Private School Network"
subtitle: "Recruiting Visits to Private High Schools by Public and Private Universities"
bibliography: ./other/burd_recruiting_chapter.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
# https://github.com/quarto-dev/quarto-cli/discussions/5853#discussioncomment-6126603
# filters:
#   - /path/to/relevel_headings.lua
---

>>>>

---
title: "The Private School Network"
subtitle: "Recruiting Visits to Private High Schools by Public and Private Universities"
author: ["Ozan Jaquette (UCLA)", "Crystal Han (NASA GeneLab)", "Irma Castañeda (MEF Associates)"]
bibliography: ./other/burd_recruiting_chapter.bib
format:
  revealjs: 
    theme: [default, ./assets/css/custom.scss]
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
    slide-level: 3
    template-partials:
      - ./assets/html/title-slide.html
include-in-header: ./assets/html/header.html
# https://github.com/quarto-dev/quarto-cli/discussions/5853#discussioncomment-6126603
# filters:
#   - /path/to/relevel_headings.lua
---
